Multi sky-view\\ 3D aerosol distribution recovery

### 2013-10-08 article.tex
Fix typo

\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to any pixel are accumulated in steps {\tt ii} and {\tt v} above.
The contributing photons that stem from just a single scattering event yield
\cref{fig:scatter_order}(a). Similarly, contributing photons that had
experienced exactly  two or three scattering events yield respectively
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
scatter yields most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long
and dense part of the atmosphere, while a vertical LOS cuts short through
the dense, lower part. Hence, toward the horizon the probability of high
order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributionS
   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}

>>>>

\Cref{fig:scatter_order} shows the contribution by successive
scattering orders. They are derived from the MC image. Photons contributing
to any pixel are accumulated in steps {\tt ii} and {\tt v} above.
The contributing photons that stem from just a single scattering event yield
\cref{fig:scatter_order}(a). Similarly, contributing photons that had
experienced exactly  two or three scattering events yield respectively
\cref{fig:scatter_order}(b) and \cref{fig:scatter_order}(c). First-order
scatter yields most of the energy in the MC image. Radiance by higher order scattering
is mostly evident at the horizon. A horizontal LOS passes through a long
and dense part of the atmosphere, while a vertical LOS cuts short through
the dense, lower part. Hence, toward the horizon the probability of high
order scattering increases.
\begin{figure}[bt]
  \centering
  \yoavcomment{\includegraphics{images/scatter_order.pdf}}
  \caption{\small Separation of the image shown in \cref{fig:mcgrid}(b) to contributions
   by successive orders of scattering: (a) first , (b) second, (c) third and (d) forth scattering order.}
  \label{fig:scatter_order}
\end{figure}
